On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-10-12 Manuscript/manuscript.tex
comments on glmm analysis

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to all the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c}
      \toprule
      Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
      \midrule
      Venue Effect Only & $-2023.5$ &   & 0.054 & $-1.871$ & 0.150\\
      Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
      Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
      \bottomrule
  \end{tabular}
\end{table}

The estimated parameters of the GLMM model from our analysis are shown in 
Table~\ref{tab:Gamma_parameters}. These statistics reflect the inclusion of 2022
in our analysis and shows the three models we considered. The standard deviation
of the heat effect is $\sigma_h$, the standard deviation of the venue effect
is $\sigma_v$, the intercept is $\alpha$ and we report $\sqrt{\phi}$ as the
square root of the dispersion parameter $\phi$
\jy{read what you wrote. These are variances not sd. Do not start a sentence
  with a symbol (see my writing guidelines).}
\of{Actually Resolved}
The GLMM with both venue and heat random effects was the best model as evidenced
by a decrease in the AIC compared to the other models with only one random effect. 
Thus, results from the GLMM with both venue and heat random effects will be 
presented throughout the rest of the paper.

\jy{do a thorough check on the captions of tables and figures.}

@@

Figure~\ref{fig:VenueEffects} shows the venue effects from 1999 to 2023 based
on the full model both with and without 2022.  As this graph does not show heat
effects, the estimates may not align exactly with the box plot presented in
figure~\ref{fig:Boxplot}.  The venue effect for 2022 is lower than any other
effect, confirming that 2022 was a low outlier.  Two aims of this section are to
determine how extreme a reaction time below 0.1 seconds is, and although the
venue effects did not differ significantly, to determine how the exclusion of 
2022 could alter the results. Using the gamma function with \texttt{link = log},
the probability of the reaction time being less than 0.1 seconds can be 
calculated in R using the methods described in Section~\ref{sec:glmm}. A 
simulation size of $10,000,000$ was chosen to estimate the probability of 
observing a reaction time below two thresholds: 0.1 and 0.08.

@@

\jy{discuss the differences between with/without 2022 data; comment on the
  pecularity of the 2022 data (as suggested by the rank based method); In a
  longer run, it may not be as strange as it looks at the first time.}
\of{Resolved}

@@

\jy{be consistent in using scienfit format of numbers; 0.0001 vs $10^{-4}$}
\of{I think we should be good now, let me know if there is anything else}

>>>>

\jy{Add the results without 2022 to this table.}
\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to all the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c}
      \toprule
      Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
      \midrule
      Venue Effect Only & $-2023.5$ &   & 0.054 & $-1.871$ & 0.150\\
      Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
      Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
      \bottomrule
  \end{tabular}
\end{table}

The estimated parameters of the GLMM model from our analysis are shown in 
Table~\ref{tab:Gamma_parameters}. These statistics reflect the inclusion of 2022
in our analysis and shows the three models we considered. The standard deviation
of the heat effect is $\sigma_h$, the standard deviation of the venue effect
is $\sigma_v$, the intercept is $\alpha$ and we report $\sqrt{\phi}$ as the
square root of the dispersion parameter $\phi$.
The GLMM with both venue and heat random effects was the best model as evidenced
by a decrease in the AIC compared to the other models with only one random
effect.
\jy{discuss the differences in the parameter estimates with and without 2022
  data, especially the sd of the random effect of venue.}

Figure~\ref{fig:VenueEffects} shows the venue effects from 1999 to 2023 based
on the full model both with and without 2022.  As this graph does not show heat
\jy{discuss the years the venue effects are high and low}
effects, the estimates may not align exactly with the box plot presented in
figure~\ref{fig:Boxplot}.  The venue effect for 2022 is lower than any other
effect, confirming that 2022 was a low outlier. \jy{but may not be as extreme as
  one would think considering the whole history.}

\jy{Hopefully, the full model is preferred for both with and without 2022}

Thus, results from the GLMM with both venue and heat random effects will be 
presented throughout the rest of the paper.

@@

Two aims of this section are to
determine how extreme a reaction time below 0.1 seconds is, and although the
venue effects did not differ significantly, to determine how the exclusion of 
2022 could alter the results. Using the gamma family with \texttt{link = log},
the probability of the reaction time being less than 0.1 seconds can be 
calculated in R using the methods described in Section~\ref{sec:glmm}. A 
simulation size of $10,000,000$ was used to estimate the probability of 
observing a reaction time below two thresholds: 0.1 and 0.08.

@@

@@
